\begin{acknowledgements}

I would like to acknowledge my advisors: Scott Shenker, Arvind
Krishnamurthy, and recently, George Necula. Scott's humility was the main reason I chose to
come to Berkeley for graduate school. He taught me, among many things, how to
transform my dry and stilted writing and speaking into engaging storylines,
and how to identify the simplicity at the core of complex technical
concepts. It is thanks to his extraordinary support that I was able to move to Seattle midway through
graduate school. Arvind is responsible for
letting me out into the academic world, and he took me under his wing again
when I returned to Seattle. His optimism and
excitement are absolutely infectious. His insistence on
surrounding
oneself with \textit{nice} collaborators has served me well throughout my
career. George is the most genuine researcher I have ever met. He does
not `play the game' nor seek to heighten his own reputation; he is motivated
as far as I can tell purely by a search for truth and value. Although I
will likely never match his raw intellect, it would be an admirable
achievement to adopt some of his attitudes.

I am also indebted to many other collaborators who have helped shaped the
content of this dissertation. First and foremost, I am indebted to my
officemate and friend Aurojit Panda. Panda's knowledge, both technical and non-technical,
is astounding. His role in shaping both of the core chapters of this
dissertation has been invaluable, and the breadth of
topics I learned about through my conversations with
him came in handy on several occasions in my 1:1 job interviews. Andreas Wundsman taught me a great deal about
how to write high quality, effective, and appropriately structured code.
Without his aid I am not sure I
would have persevered through my third year of graduate school. Sam Whitlock,
Ahmed El-Hassany, Vjekoslav Brajkovic, Zhi Liu, Andrew Or, Jefferson Lai,
Eugene Huang, Kyriakos Zarifis, and Barath Raghavan also played an
instrumental role in helping me shape the ideas and results presented here.

Vern Paxson, Ali Ghodsi, and Barath Raghavan, each in their own way, taught me
the value and importance of focusing on details. My competency as a researcher
has been improved by their urging.

When I first met Ethan Katz-Bassett, I did not yet know that `dictionary' is
synonym for `hashmap', and when he gave me instructions for running my first experiment,
I mistakenly believed that he was asking me to take
out pen and paper and painstakingly count IP addresses by hand. Thanks to his
mentorship, I was able to successfully start along the path to where I am today.
In my own work with undergraduates I have tried to emulate his innate
mentorship skills.

My persective on academia and its role in the world has been shaped by my
multiple experiences as a software engineering intern. Michael Piatek,
Michael Buettner, and Teemu Koponen served as great mentors and role models during that time.

Among my graduate student peers I have found some of my dearest friends.
Justine Sherry has provided great mentorship, example-setting, and rapport
since my junior year of college. I shared many laughs with my Berkeley officemates
Radhika Mittal, Kay Ousterhout, Amin Tootoonchian, Murphy Mccauley, Ethan
Jackson, Qifan Pu, Wenting Zheng, and (de
facto) Shivaram Venkataraman, as well as my UW officemates Will Scott, Qiao
Zhang, Danyang Zhou, Vincent Liu, Haichen Shen, Seungyeop Han, Donny Huang, Ray Cheng, and Sophia Wang.
Sangjin Han has perhaps the highest signal (insight) to noise (gossip)
ratios of anyone I know. Peter Bailis, through his example, taught me the
value of promoting one's research, especially to non-academic audiences.
I will never forget my housemates, especially Austin Buchan, Armin
Samii, Ali K\"oksal, and Martin Maas.

I would be remiss not to thank Maria Clow, who continues to teach
me to be a better person. I have cherished her companionship through
many experiences, even a Category 4 hurricane.

Lastly, I am grateful to my family for their love and support.

% Many thanks to the STS team for making this thesis possible: Andreas Wundsam,
% Barath Raghavan, Aurojit Panda, Zhi Liu, Sam Whitlock, Ahmed
% El-Hassany, Andrew Or, Jefferson Lai, Eugene Huang, Hrishikesh Acharya, and
% Kyriakos Zarifis.
%
% \noindent~Thanks also to Shivaram Venkataraman, Justine Sherry, Radhika Mittal, Teemu
% Koponen, and Peter Bailis for providing feedback on earlier versions of this
% text.
%
% \noindent~Most importantly, huge thanks to Scott Shenker for putting up with me!

% - I'll start with the person who let me out into the academic world: Arvind Krishnamurthy. Arvind's optimism and excitement is absolutely infectuous. And his insistence on surrounding himself by *nice* people has carried over well into the remainder of my collaborators.
% - Ethan Katz-Bassett for starting my on research.
% - George is among the most pure, authentic researchers I know. Super nice.
% - Ali Ghodsi " Appreciate the value of both the forest and the trees"
% - Scott, for putting up with me, supporting me in moving to Seattle,...
% - Justine for the mentorship, example-setting, and friendship she has given me since my junior year of college.
% - Vern Paxson and Barath Raghavan for encouraging me to pay attention to details
% - Aurojit Panda for his knowledge and persistent willingness to help.
% - Sangjin Han, who has the highest signal (insight) to noise
%   (gossip) ratio of anyone I have ever met.
% - Maria for helping me become a better person, and for putting up with a
%   boyfriend who travels all the time.

%  Your advisor is a human being

%  Alt title: contrarian, inflammatory remarks aren’t the only nor best way to
%  engage an audience
%
%  Seek out people who complement your skills & expertise
%
%  Corollary: make use of your advisor
%
%  Corollary: present your work to practitioners, aggressively seek out
%  feedback.
%  Thanks to Peter Bailis for setting an example?
%
% Thanks to the undergraduates I worked with:
%  Give your undergraduate mentees autonomy over their own HotNets-sized
%  project. Make them first author.

% JAmshed for his positivity / optimism?

\end{acknowledgements}
