\noindent\textbf{Applying \sys to Production Systems.} Our work has primarily focused on minimizing bug traces found using fuzz testing performed as a part of the QA process. In particular, \sys requires that bug traces include causal dependencies between messages, and our implementation requires that the application be run on a single physical machine to record this information. However, since the causal information required by \sys is only required to establish a partial order between messages, recording causal dependencies does not require coordination between the different actors running in a system. Given a per-actor log, which records the order in which the actor processed received messages, and the set of messages sent while processing each message, we can reconstruct the causal dependency graph between messages and hence run minimization using \sys. Recording a sufficiently detailed log for each actor adds some logging overhead, however this overhead is modest and involves no additional messages or coordination and can be reasonably deployed in production. Therefore, with sufficient logging \sys can be used to debug both bug traces generated during QA tests and from production failures.

\noindent\textbf{\sys and Deterministic Replay.} Prior work~\cite{} has described a variety of systems that support deterministic replay of applications for debugging and other purposes. While deterministic replay by itself is not sufficient for minimization, it forms a key component of DPOR, which we use for schedule enumeration and exploration. \sys can be implemented on top of a deterministic replay system, by adding algorithms for schedule enumeration, schedule prioritization and minimization, the final two of which are our primary contribution. In this work, we built a replay system using AspectJ, rather than making use of an existing deterministic replay system since we could not find a suitably supported system that could be used with Akka or other actor based systems. Despite the rich academic literature in this area, we have not seen many shipping systems implement deterministic replay, and we hope our results inspire more interest in building such systems.